\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Navid}{Hasan}{
\descript{Software Engineering Undergrad\centering\vspace{3pt}}
\href{mailto:navidsustswe03@gmail.com}{\bf navidsustswe03@gmail.com }| \bf +8801621182527 | \bf 
 Dhaka, Bangladesh}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.4\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\linesep
\runsubsection{Shahjalal University of Science and Technology}\\
\descript{\href{https://www.sust.edu/institutes/iict/curriculum}{B.Sc. in Software Engineering, IICT}}
\small Jan 2019 - Present | Sylhet, Bangladesh\\
\vspace{2pt}
\textbf{CGPA: 3.60 (Till 6th Semester)} \\
\vspace{5pt}
\runsubsection{St. Joseph Higher Secondary School}\\
\descript{Higher Secondary School Certificate}
\small July 2016 - July 2018 | Dhaka, Bangladesh\\
\vspace{2pt}
\textbf{GPA: 5.00}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\linesep
\textbf{GitHub:// }\descript{\href{https://github.com/navid-hasan26}{\textbf{navid-hasan26}}}
\vspace{2pt}
\small \textbf{LinkedIn:// }\descript{\href{https://www.linkedin.com/in/navid-hasan26/}{Navid Hasan}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROBLEM SOLVING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Problem Solving}
\linesep
\small\textbf{StopStalk:// }\descript{\href{https://www.stopstalk.com/user/profile/navid_hasan}{\textbf{navid-hasan}}}
\vspace{2pt}
\small \textbullet{} \textbf{250+} solves in \href{https://codeforces.com/profile/navid_hasan}{\descript {CodeForces}}.
\hspace{-5pt}\textbullet{} Around \textbf{400} total solves in various OJs.\\
\textbullet{} Participated in various Programming Contests
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\linesep
\textbullet\textbf{5th place} in \textbf{Tech Storm 4 Hackathon} at Leading University, Sylhet out of 30+ teams; November 2021\\
\vspace{3pt}
\textbullet\textbf{7th place} in \textbf{bdapps National Hackathon 2022 Regional Round 3: Sylhet} out of 100+ teams; August 2022\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\linesep
\runsubsection{Technical Skills}\\
\textbullet{\textbf{Language}}\\
\vspace{3pt}
\fbox {Java} \hspace{1pt} \fbox{Python} \hspace{1pt}  \fbox{JavaScript} \hspace{1pt} \fbox{C/C++} \\
\vspace{2pt}
\textbullet{\textbf{Frontend}}\\
\vspace{5pt}
\fbox {HTML5} \hspace{1pt} \fbox{CSS3} \hspace{1pt}  \fbox{ReactJS} \hspace{1pt}  \fbox{BootStrap}\\
% \vspace{2pt}
\textbullet{\textbf{Backend}}\\
\vspace{5pt}
\fbox {Node.js} \hspace{1pt} \fbox{Express}\\
\vspace{3pt}
\textbullet{\textbf{Database}}\\
\vspace{5pt}
\fbox  {MySql} \hspace{1pt} \fbox{PostgreSQL}\\
\vspace{3pt}
\textbullet{\textbf{Additional Tools}}\\
\vspace{5pt}
\fbox{Git} \hspace{1pt}  \fbox{Github} \hspace{1pt} \fbox{LaTeX } \\
\vspace{7pt}

\runsubsection{Soft Skills}\\
\small \textbullet{} Ability to work as a team\\
\textbullet{} Team Leadership\\
\textbullet{} Public Speaking\\
\textbullet{} Initiator to solve a problem\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.57\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\linesep

\runsubsection{Story Minder}
\descript{| \href{https://github.com/navid-hasan26/Story-Minder-Desktop-}{Github}}
\vspace{2pt}
\textbullet{}Qt \textbullet{} C++\\
\location{\hspace{5mm} An interactive windows application built in Qt Creator for personal journal writing.}
\vspace{10pt}
\begin{tightemize}
    \item Built in collaboration with \href{https://selisegroup.com/}{\textbf{SELISE Digital Platforms;}} July 2019, where I was introduced to \textbf{technologies such as git, GitHub, BitBucket, and development processes like agile development.}
    \item Crated the \textbf{user registration and login process} where user can create their own account.
    \item Users can keep entries of their day-to-day life and important notes.
\end{tightemize}
\sectionsep
\vspace{3pt}

\runsubsection{Hall Management System}
\descript{| \href{https://github.com/navid-hasan26/hall_management_system}{Github }| \href{https://www.overleaf.com/read/pzwvbnmdmgcw}{Report}}
\vspace{2pt}
\textbullet{} JavaScript \textbullet{} ReactJS \textbullet{} Node.js\textbullet{} Express.js \textbullet{}MySql\\
\location{\hspace{5mm} A web-based application to bring the university's hall management system online and easier for both students and administrations.}
\begin{tightemize}
    \item Implemented \textbf{access level} for different types of users in the backend.
    \item Students can \textbf{apply, check the status of their application, and file complaints} by creating an account.
    \item Administrations can handle students' \textbf{room allocation and related charges.}
    \item Resolve issues created by the students.
\end{tightemize}
\sectionsep
\vspace{3pt}

\runsubsection{News Blog}
\descript{| \href{https://github.com/navid-hasan26/News-Blog-CRUD}{Github}}
\vspace{2pt}
\textbullet{} ReactJS \textbullet{} Node.js \textbullet{}Express.js \textbullet{}MySql\\
\location{\hspace{5mm} An online blog posting website where users can read the topics they are interested in and also post their own stories.}
\begin{tightemize}
    \item Created \textbf{Login and Sign Up authentication} for users.
    \item Implemented \textbf{article posting and reading module.}
\end{tightemize}
\sectionsep
\vspace{3pt}

\runsubsection{Kutir}(Hackathon Project )
\descript{| \href{https://github.com/navid-hasan26/Kutir-LU-Hack}{Github}}
\vspace{2pt}
\textbullet{} JavaScript \textbullet{}BootStrap \textbullet{} HTML5 \textbullet{} CSS3 \textbullet{}FireStore\\
\location{\hspace{5mm} An online E-commerce platform for ethnic goods where sellers can put their products for bidding in single or bulk amounts and buyers can bid to buy.}
\sectionsep
\vspace{3pt}

\runsubsection{Rokto Lagbe}
\descript{| \href{https://github.com/navid-hasan26/rokto-lagbe}{Github}}
\vspace{2pt}
\textbullet{}React Native \textbullet{} Node.js \textbullet{} Express.js \textbullet{}PostgreSQL\\
\location{\hspace{5mm} A mobile application to request emergency blood in a certain radius of the user's location as well as look for live requests to donate blood on their own.}
\sectionsep

% \runsubsection{Rokto Lagbe}
% \descript{| \href{}{Github}}
% \textbullet{}React Native \textbullet{} Node.js \textbullet{} Express.js \textbullet{}PostgreSQL\\
% \location{\hspace{5mm} A mobile application to request emergency blood in a certain radius of the user's location as well as look for the live request to donate blood on their own.}
% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    CO-CURRICULAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Co-Curricular} 
\linesep
\vspace{-5pt}
\begin{tightemize}
\item \textbf{Organizing Committee} at \textbf{SUST SWE Technovent 2023,} IICT, SUST;
January 2023
\item \textbf{Volunteer} at \textbf{LICT Techfest,} IICT, SUST;
March 2019.
\item \textbf{Corresponding Secretary} at Josephite math club;
October 2017.\\
(Organized \textbf{Josephite Math Mania, 2017})
\item \textbf{Board Member} at Scintilla Science Club; October 2017.\\
(Organized \textbf{61st Annual Science Festival, 2017})
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    HOBBIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Hobbies}
% \linesep
% \vspace{-5pt}
% \begin{tightemize}
% \item Being up to date with recent tech trends
% \item Reading Fictional and Non-Fictional Books
% \item Traveling, Trekking
% \end{tightemize}
% \sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
